Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
one more para in 4.0

@@

We captures the set of operators that every cast representation must provide 
with \emph{cast abstract data type} (Definition~\ref{def:cast-rep}). 
The first three operators allow a language implementation to construct casts. 
So we call them \textit{cast constructors}. And the forth and last operator 
allows the implementation to apply casts onto values.

>>>>

If $C$, an implementation of the Cast ADT inteface, satisifies a collection of 
properties that we defined as Lazy D Cast ADT. We can instantiate our framework 
theorem that we define shortly to prove that evaluating an program in 
\effCEK{C} gives the same result as \ineffCEKD. We are working on a
similar theorem for \lazyUD{}.

\todo[inline]{UNDER CONSTRUCTION. -KC}

@@

We captures the set of operators that every cast representation must provide 
with \emph{cast abstract data type} (Definition~\ref{def:cast-rep}). 
The first three operators allow \effCEK{C} to construct casts. 
So we call them \textit{cast constructors}. And the forth and last operator 
allows \effCEK{C} to apply casts onto values.
